---
title: "p8105_hw6_cw3370.Rmd"
output: 
  github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(broom)
library(knitr)
library(modelr)
library(corrplot)
library(leaps)
```

# Problem 1

**Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).**

Data Description
```{r}
birthweight <- read_csv("data/birthweight.csv")  
skimr::skim(birthweight)
```

```{r message=FALSE}
birthweight_df <- 
  birthweight %>% 
  mutate(
    babysex = factor(babysex,
                     levels = c(1,2),
                     labels = c("male","female")),
    frace = factor(frace,
                   levels = c(1,2,3,4,8,9),
                   labels = c("White","Black","Asian","Puerto Rican","Other","Unkown")),
    malform = factor(malform,
                     levels = c(0,1),
                     labels = c("absense","present")),
    mrace = factor(mrace,
               levels = c(1,2,3,4,8),
               labels = c("White","Black","Asian","Puerto Rican","Other"))
) %>% 
  drop_na()

```

**Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.**

l used backward elimination to get the model, the variable are babysex, bhead, blength, delwt, fincome, gaweeks, mheight, ppwt, smoken
```{r eval=FALSE}
mult.fit = lm(bwt ~ ., data = birthweight_df)
summary(mult.fit)

step1 = update(mult.fit, . ~ . -frace)
summary(step1)

step2 = update(step1, . ~ . -malform)
summary(step2)

step3 = update(step2, . ~ . -ppbmi)
summary(step3)

step4 = update(step3, . ~ . -momage)
summary(step4)

step5 = update(step4, . ~ . -menarche)
summary(step5)

step6 = update(step5, . ~ . -mrace)
summary(step6)

step7 = update(step6, . ~ . -pnumlbw)
summary(step7)

step8 = update(step7, . ~ . -pnumsga)
summary(step8)

step9 = update(step8, . ~ . -wtgain)
summary(step9)

step10 = update(step9, . ~ . -parity)
summary(step10)


```

```{r}
fit <- lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + ppwt + smoken, data =birthweight_df)

birthweight_df %>%
  modelr::add_residuals(fit) %>%
  modelr::add_predictions(fit) %>%
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.3)
```



```{r}
cv_df = 
  crossv_mc(birthweight_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) %>% 
  mutate(
    my_mod         = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + ppwt + smoken, data = .x)),
    bl_ga_mod      = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    bh_bl_sex_mod  = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x)) 
    ) %>% 
  mutate(
    rmse_my        = map2_dbl(my_mod        , test, ~rmse(model = .x, data = .y)),
    rmse_bl_ga     = map2_dbl(bl_ga_mod     , test, ~rmse(model = .x, data = .y)),
    rmse_bh_bl_sex = map2_dbl(bh_bl_sex_mod , test, ~rmse(model = .x, data = .y))
    )

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

# Problem 2
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
get_r <- function(fit){
  r <- 
    fit %>% 
    broom::glance() %>% 
    pull(r.squared)
  
  return(r)
}

get_log <- function(fit){
  estimate = 
  fit %>% 
    broom::tidy() %>% 
    pull(estimate)
  
  log = log10(prod(estimate) )
  
  return(log)
}

boot_straps <-  
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    r_squared = unlist(map(models,get_r)),
    log = unlist(map(models,get_log))
  ) %>% 
  select(-strap,-models)

boot_straps %>% 
  ggplot(aes(x = r_squared))+
  geom_density()

boot_straps %>% 
  ggplot(aes(x = log))+
  geom_density()
```

```{r}
boot_straps %>% 
  summarize(
    r_low = quantile(r_squared,probs = c(0.025)),
    r_high = quantile(r_squared,probs = c(0.0975))
  ) %>% 
  knitr::kable()

boot_straps %>% 
  summarize(
    r_low = quantile(log,probs = c(0.025)),
    r_high = quantile(log,probs = c(0.0975))
  )%>% 
  knitr::kable()
```

